Constraint result to the self-interacting dark matter model without dark energy in cosmology

### 2025-04-14 article/article.tex
update to desi dr2

   \author{Yixuan Zhu}\affiliation{Department of Astronomy, Beijing Normal University.
   Beijing 100875.
   PR China}

@@

   To constrain the relevant IDM models (\cite{Basilakos_2009}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001, Daniel.Stern_2010, 
   M.Moresco_2012, Zhang_2014, Moresco_2016, 10.1093/mnras/stx301, 10.1093/mnrasl/slv037, 
   Borghi_2022, Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the quasar data from \cite{Lusso_2020}, 
   the BAO data from SDSS (\cite{PhysRevD.103.083533}) and DESI 2024 
   (\cite{desicollaboration2024desi2024vicosmological}).

@@

   It is widely known that the Hubble parameter $H(z)$ depends on
   the differential age as a function of redshift $z$ in the form
   \begin{equation}
      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},\label{eq:12}
   \end{equation}
   which provides a direct measurement on $H(z)$ based on
   $\mathrm{d}z/\mathrm{d}t$.
   OHD measurements have recently been acquired mainly employing
   cosmic chronometers (CC). The CC method is used to provide 33 observational
   data points, which are taken in the redshift range [0.07, 1.965].
   The Table \ref{tab:1} lists the OHD dataset used in this analysis.
   In this case, $\chi^2$ can be defined as
   \begin{equation}
      \chi_{\text{OHD}}^2=\sum_i^{33}\frac{(H_{\text{th}}-H_{\text{data}})^2}{\sigma_i^2}.
   \end{equation}

   \begin{table}[htbp]
      \centering
      \begin{tabular}{llll}
         \hline\hline
         $z$ & $H(z)$ & Reference \\
         \hline     
         0.07 & 69$\pm$19.6 & \cite{Zhang_2014} \\
         0.09 & 69$\pm$12 & \cite{PhysRevD.71.123001} \\
         0.12 & 68.6$\pm$26.2 & \cite{Zhang_2014} \\
         0.17 & 83$\pm$8 & \cite{PhysRevD.71.123001} \\
         0.179 & 75$\pm$4 & \cite{M.Moresco_2012} \\
         0.199 & 75$\pm$5 & \cite{M.Moresco_2012} \\
         0.2 & 72.9$\pm$29.6 & \cite{Zhang_2014} \\
         0.27 & 77$\pm$14 & \cite{PhysRevD.71.123001} \\
         0.28 & 88.8$\pm$36.6 & \cite{Zhang_2014} \\
         0.352 & 83$\pm$14 & \cite{M.Moresco_2012} \\
         0.3802 & 83$\pm$13.5 & \cite{Moresco_2016}  \\
         0.4 & 95$\pm$17 & \cite{PhysRevD.71.123001} \\
         0.4004 & 77$\pm$10.2 & \cite{Moresco_2016} \\
         0.4247 & 87.1$\pm$11.2 & \cite{Moresco_2016} \\
         0.4497 & 92.8$\pm$12.9 & \cite{Moresco_2016} \\
         0.47 & 89$\pm$34 & \cite{10.1093/mnras/stx301} \\
         0.4783 & 80.9$\pm$9 & \cite{Moresco_2016} \\
         0.48 & 97$\pm$62 & \cite{Daniel.Stern_2010} \\
         0.593 & 104$\pm$13 & \cite{M.Moresco_2012} \\
         0.68 & 92$\pm$8 & \cite{M.Moresco_2012} \\
         0.75 & 98.8$\pm$33.6 & \cite{Borghi_2022} \\
         0.781 & 105$\pm$12 & \cite{M.Moresco_2012} \\
         0.8 & 113.1$\pm$15.1 & \cite{Jiao_2023} \\
         0.875 & 125$\pm$17 & \cite{M.Moresco_2012} \\
         0.88 & 90$\pm$40 & \cite{Daniel.Stern_2010} \\
         0.9 & 117$\pm$23 & \cite{PhysRevD.71.123001} \\
         1.037 & 154$\pm$20 & \cite{M.Moresco_2012} \\
         1.3 & 168$\pm$17 & \cite{PhysRevD.71.123001} \\
         1.363 & 160$\pm$33.6 & \cite{10.1093/mnrasl/slv037} \\
         1.43 & 177$\pm$18 & \cite{PhysRevD.71.123001} \\
         1.53 & 140$\pm$14 & \cite{PhysRevD.71.123001} \\
         1.75 & 202$\pm$40 & \cite{PhysRevD.71.123001} \\
         1.965 & 186.5$\pm$50.4 & \cite{10.1093/mnrasl/slv037} \\
         \hline    
      \end{tabular}
      \caption{The OHD dataset from different paper.}
      \label{tab:1}
   \end{table}

@@

   We use the fiducial SNe Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
   host distances (\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
   give the $\chi^2$ as 
   \begin{equation}
      \chi_{\text{SNe}}^2=\Delta^{\text{T}}C^{-1}\Delta,
   \end{equation}
   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
   covariance matrix of the SNe Ia data, the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
   luminosity distance $d_L$ can be given as a function of redshift $z$
   \begin{equation}
      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.\label{eq:15}
   \end{equation}
   To eliminate the advanced restriction to $H_0$ from $M_b$, we adopt
   the likelihood function as
   \begin{equation}
      \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
   \end{equation}
   where $B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
   Apparently, these two functions give the same constraints in $\Omega_{2,0}$ and
   $\log_{10}(\kappa C_1)$.

@@

   The $L_X-L_{UV}$ relation of quasar is usually written as
   \begin{equation}
      \log_{10}(L_X)=\beta+\gamma\log_{10}(L_{UV}),
   \end{equation}
   which gives that
   \begin{eqnarray}
      \nonumber\log_{10}(F_X)&=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
                    \\ &+2(\gamma-1)\log_{10}(d_L),
   \end{eqnarray}
   where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
   Here we use the parameters defined in \cite{li2024redshiftevolutionxrayuv}, which
   gives\begin{equation}
      \beta=\beta_0+\beta_1(1+z),\gamma=\gamma_0+\gamma_1(1+z),
   \end{equation}
   so the $\chi^2$ function for the QSO data can be defined as
   \begin{equation}
      \chi_{\text{QSO}}^2=\sum_i^{2421}\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
      -\ln(2\pi s_i^2)\right],
   \end{equation}
   where $s_i^2=\mathrm{d}y_i^2+\gamma^2\mathrm{d}x_i^2+\delta^2$ refers to the 
   uncertainties on the $x_i\ (\log_{10}F_X)$ and $y_i\ (\log_{10}F_{UV})$ and
   $\delta_i$ reprensent the instrinsic dispersion.

@@

   The Baryon acoustic oscillation (BAO) method provides a key cosmological probe
   sensitive to the cosmic expansion history with well-controlled systematics.
   We use two BAO datasets from the SDSS (\cite{PhysRevD.103.083533}) and DESI 2024 (\cite{desicollaboration2024desi2024vicosmological}),
   which are given at Table \ref{tab:2} and Table \ref{tab:3}, respectively.
   The redshift is up to 2.33 both in the SDSS and the DESI 2024 dataset.

@@

   However, the solution of Eq.(\ref{eq:8}) only gives an upper limit of redshift $z_{\max}$
   (see Appendix), and we just try to use the cross
   parameter $r_{\text{d}}h$ to give the constraints.

   \begin{table}[htbp]
      \centering
      \begin{tabular}{llll}
         \hline\hline
         $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & 
         $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
         \hline
         0.15 & & & 4.47$\pm$0.17 \\
         0.38 & 10.23$\pm$0.17 & 25$\pm$0.76 & \\
         0.51 & 13.36$\pm$0.21 & 22.33$\pm$0.58 & \\
         0.7 & 17.86$\pm$0.33 & 19.33$\pm$0.53 & \\
         0.85 & & & $18.33_{-0.62}^{+0.57}$ \\
         1.48 & 30.69$\pm$0.8 & 13.26$\pm$0.55 & \\
         2.33 & 37.6$\pm$1.9 & 8.93$\pm$0.28 & \\
         2.33 & 37.3$\pm$1.7 & 9.08$\pm$0.34 & \\
         \hline
      \end{tabular}
      \caption{The BAO-only dataset from SDSS. The $\sigma$ of asymmetric 
      uncertainties would be calculated on average.}
      \label{tab:2}
   \end{table}

   \begin{table}[htbp]
      \centering
      \begin{tabular}{llll}
         \hline\hline
         $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & 
         $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
         \hline
         0.295 & & & 7.93$\pm$0.15 \\
         0.51 & 13.62$\pm$0.25 & 20.98$\pm$0.61 & \\
         0.706 & 16.85$\pm$0.32 & 20.08$\pm$0.6 & \\
         0.93 & 21.71$\pm$0.28 & 17.88$\pm$0.35 & \\
         1.317 & 27.79$\pm$0.69 & 13.82$\pm$0.42 & \\
         1.491 & & & 26.07$\pm$0.67 \\
         2.33 & 39.71$\pm$0.94 & 8.52$\pm$0.17 & \\
         \hline
      \end{tabular}
      \caption{The BAO dataset from DESI 2024.}
      \label{tab:3}
   \end{table}

@@

   For the BAO dataset, we use $h \simeq 0.7$ as the default value to give constraints.

@@

   We use the 97.7\% and 2.3\% quantiles (about $2\sigma$) to determine the upper and lower
   limits of the parameters. The  constraint results are shown in 
   Figure \ref{fig:1}-\ref{fig:6} and summarized in Table \ref{tab:5}.

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_2.pdf}
      }
      \caption{The constraint result from the supernovae
      Ia data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_qso_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_qso_2.pdf}
      }
      \caption{The constraint result from the SNe Ia + QSO data.}
   \end{figure}

   We could find that the combined result of SNe Ia and QSO is most
   similar to SNe Ia result, what may refer that the QSO cannot
   give an effective constraint. It may be due to the data quality
   at the high redshift, while the effective redshift of QSO as tracers in BAO
   is about 1.5, within the SNe Ia range.

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_2.pdf}
      }
      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
      \label{fig:6}
   \end{figure}

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 1 & OHD & SNe Ia & SNe Ia + QSO & BAO &
          OHD + SNe Ia & OHD + SNe Ia + BAO \\
         \hline
         $\Omega_{2,0}$ & $0.321_{-0.067}^{+0.055}$ & $0.360_{-0.020}^{+0.020}$
          & $0.359_{-0.020}^{+0.020}$ & $0.301_{-0.013}^{+0.013}$
          & $0.330_{-0.016}^{+0.016}$ & $0.313_{-0.010}^{+0.010}$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.17$ & $<-2.51$ & $<-2.57$
          & $<-3.10$ & $<-2.88$ & $<-3.39$ \\
         $\log_{10}(M_x/$GeV) & $>-9.77$ & $>-9.42$ & $>-9.40$
          & $>-8.84$ & $>-9.03$ & $>-8.52$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 1.}
      \label{tab:5}
   \end{table*}

@@

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 2 & OHD & SNe Ia & SNe Ia + QSO & BAO &
          OHD + SNe Ia & OHD + SNe Ia + BAO \\
         \hline
         $\Omega_{2,0}$ & $0.295_{-0.077}^{+0.077}$ & $0.216_{-0.078}^{+0.096}$
          & $0.208_{-0.087}^{+0.12}$ & $0.296_{-0.014}^{+0.014}$
          & $0.202_{-0.049}^{+0.060}$ & $0.291_{-0.013}^{+0.013}$ \\
         $n$ & $1.4_{-2.8}^{+1.4}$ & $-0.82_{-0.44}^{+0.29}$
          & $-0.85_{-0.49}^{+0.42}$ & $-0.40_{-0.29}^{+0.29}$
          & $-0.83_{-0.27}^{+0.24}$ & $-0.41_{-0.13}^{+0.13}$ \\
         $w_{\text{IDM}}$ & $-1.5_{-0.9}^{+0.5}$ & $-0.73_{-0.15}^{+0.10}$
          & $-0.72_{-0.16}^{+0.14}$ & $-0.87_{-0.10}^{+0.10}$
          & $-0.72_{-0.09}^{+0.09}$ & $-0.86_{-0.04}^{+0.04}$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 2.}
      \label{tab:6}
   \end{table*}

>>>>

   \author{Yixuan Zhu}\affiliation{Department of Astronomy, Beijing Normal University,
   Beijing 100875, China}

@@

   To constrain the relevant IDM models (\cite{Basilakos_2009}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001, Daniel.Stern_2010, 
   M.Moresco_2012, Zhang_2014, Moresco_2016, 10.1093/mnras/stx301, 10.1093/mnrasl/slv037, 
   Borghi_2022, Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the quasar data from \cite{Lusso_2020}, 
   the BAO data from SDSS-IV (\cite{PhysRevD.103.083533}) and DESI DR2 
   (\cite{desicollaboration2025desidr2resultsii}).

@@

   It is widely known that the Hubble parameter $H(z)$ depends on
   the differential age as a function of redshift $z$ in the form
   \begin{equation}
      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},\label{eq:12}
   \end{equation}
   which provides a direct measurement on $H(z)$ based on
   $\mathrm{d}z/\mathrm{d}t$.
   OHD measurements have recently been acquired mainly employing
   cosmic chronometers (CC). The CC method is used to provide 33 observational
   data points, which are taken in the redshift range [0.07, 1.965].
   The Table \ref{tab:1} lists the OHD dataset used in this analysis.
   In this case, $\chi^2$ can be defined as
   \begin{equation}
      \chi_{\text{OHD}}^2=\sum_i\frac{(H_{\text{th}}-H_{\text{data}})^2}{\sigma_i^2}.
   \end{equation}

   \begin{table}[htbp]
      \centering
      \begin{tabular}{ccl}
         \hline\hline
         $z$ & $H(z)$ & Reference \\
         \hline     
         0.07 & $69 \pm 19.6$ & \cite{Zhang_2014} \\
         0.09 & $69 \pm 12$ & \cite{PhysRevD.71.123001} \\
         0.12 & $68.6 \pm 26.2$ & \cite{Zhang_2014} \\
         0.17 & $83 \pm 8$ & \cite{PhysRevD.71.123001} \\
         0.179 & $75 \pm 4$ & \cite{M.Moresco_2012} \\
         0.199 & $75 \pm 5$ & \cite{M.Moresco_2012} \\
         0.2 & $72.9 \pm 29.6$ & \cite{Zhang_2014} \\
         0.27 & $77 \pm 14$ & \cite{PhysRevD.71.123001} \\
         0.28 & $88.8 \pm 36.6$ & \cite{Zhang_2014} \\
         0.352 & $83 \pm 14$ & \cite{M.Moresco_2012} \\
         0.3802 & $83 \pm 13.5$ & \cite{Moresco_2016}  \\
         0.4 & $95 \pm 17$ & \cite{PhysRevD.71.123001} \\
         0.4004 & $77 \pm 10.2$ & \cite{Moresco_2016} \\
         0.4247 & $87.1 \pm 11.2$ & \cite{Moresco_2016} \\
         0.4497 & $92.8 \pm 12.9$ & \cite{Moresco_2016} \\
         0.47 & $89 \pm 34$ & \cite{10.1093/mnras/stx301} \\
         0.4783 & $80.9 \pm 9$ & \cite{Moresco_2016} \\
         0.48 & $97 \pm 62$ & \cite{Daniel.Stern_2010} \\
         0.593 & $104 \pm 13$ & \cite{M.Moresco_2012} \\
         0.68 & $92 \pm 8$ & \cite{M.Moresco_2012} \\
         0.75 & $98.8 \pm 33.6$ & \cite{Borghi_2022} \\
         0.781 & $105 \pm 12$ & \cite{M.Moresco_2012} \\
         0.8 & $113.1 \pm 15.1$ & \cite{Jiao_2023} \\
         0.875 & $125 \pm 17$ & \cite{M.Moresco_2012} \\
         0.88 & $90 \pm 40$ & \cite{Daniel.Stern_2010} \\
         0.9 & $117 \pm 23$ & \cite{PhysRevD.71.123001} \\
         1.037 & $154 \pm 20$ & \cite{M.Moresco_2012} \\
         1.3 & $168 \pm 17$ & \cite{PhysRevD.71.123001} \\
         1.363 & $160 \pm 33.6$ & \cite{10.1093/mnrasl/slv037} \\
         1.43 & $177 \pm 18$ & \cite{PhysRevD.71.123001} \\
         1.53 & $140 \pm 14$ & \cite{PhysRevD.71.123001} \\
         1.75 & $202 \pm 40$ & \cite{PhysRevD.71.123001} \\
         1.965 & $186.5 \pm 50.4$ & \cite{10.1093/mnrasl/slv037} \\
         \hline    
      \end{tabular}
      \caption{The OHD dataset from different reference.}
      \label{tab:1}
   \end{table}

@@

   We use the fiducial SNe Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
   host distances (\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
   give the $\chi^2$ as 
   \begin{equation}
      \chi_{\text{SNe}}^2=\Delta C^{-1} \Delta^{\text{T}},
   \end{equation}
   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
   covariance matrix of the SNe Ia data, the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
   luminosity distance $d_L$ can be given as a function of redshift $z$
   \begin{equation}
      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.\label{eq:15}
   \end{equation}
   To eliminate the advanced restriction to $H_0$ from $M_b$, we adopt
   the likelihood function as
   \begin{equation}
      \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{\mathcal{C}}+\ln\left(\frac{\mathcal{C}}{2\pi}\right),
   \end{equation}
   where $B$ is the sum of $\Delta C^{-1}$ and $\mathcal{C}$ is the sum of $C^{-1}$.

@@

   The $L_X-L_{UV}$ relation of quasar is usually written as
   \begin{equation}
      \log_{10}(L_X)=\beta+\gamma\log_{10}(L_{UV}),
   \end{equation}
   which gives that
   \begin{eqnarray}
      \nonumber\log_{10}(F_X)&=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
                    \\ &+2(\gamma-1)\log_{10}(d_L),
   \end{eqnarray}
   where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
   Here we use the parameters defined in \cite{li2024redshiftevolutionxrayuv}, which
   gives\begin{equation}
      \beta=\beta_0+\beta_1(1+z),\gamma=\gamma_0+\gamma_1(1+z),
   \end{equation}
   so the $\chi^2$ function for the QSO data can be defined as
   \begin{equation}
      \chi_{\text{QSO}}^2=\sum_i\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
      -\ln(2\pi s_i^2)\right],
   \end{equation}
   where $s_i^2=\mathrm{d}y_i^2+\gamma^2\mathrm{d}x_i^2+\delta^2$ refers to the 
   uncertainties on the $x_i\ (\log_{10}F_X)$ and $y_i\ (\log_{10}F_{UV})$ and
   $\delta_i$ reprensent the instrinsic dispersion.

@@

   The Baryon acoustic oscillation (BAO) method provides a key cosmological probe
   sensitive to the cosmic expansion history with well-controlled systematics.
   We use two BAO datasets from the SDSS-IV (\cite{PhysRevD.103.083533}) and 
   DESI DR2 (\cite{desicollaboration2025desidr2resultsii}),
   which are given at Table \ref{tab:2} and Table \ref{tab:3}, respectively.
   The redshift is up to 2.33 both in the SDSS and the DESI 2024 dataset.

@@

   However, the solution of Eq.(\ref{eq:8}) only gives an upper 
   limit of redshift $z_{\max}$ (see Appendix), and the cross 
   parameter $r_{\text{d}}h$ is used to give the constraints.

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
         \hline
      \end{tabular}
      \caption{The BAO+RSD measurements dataset from SDSS-IV.}
      \label{tab:2}
   \end{table*}

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
         Lya & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
         \hline
         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
         \hline
      \end{tabular}
      \caption{The BAO dataset from DESI DR2.}
      \label{tab:3}
   \end{table*}

@@

   For the dataset which cannot give a constraint to $H_0$, 
   we use $h \simeq 0.7$ as the default value to calculate the 
   dark matter particle mass $M_x$

@@

   We use the 97.7\% and 2.3\% quantiles (about $2\sigma$) to determine the upper and lower
   limits of the parameters. The  constraint results are shown in 
   Figure \ref{fig:1}-\ref{fig:5} and summarized in Table \ref{tab:5}.

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{compare_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{compare_2.pdf}
      }
      \caption{The constraint result from the supernovae Ia data
      compared with the SNe Ia+QSO data.}
   \end{figure}

   We could find that the combined result of SNe Ia and QSO is quite
   similar to SNe Ia result, what may refer that the QSO cannot
   give an effective constraint. It may be due to the data quality
   at the high redshift, while the effective redshift of QSO as tracers in BAO
   is about 1.5, respectively, within the SNe Ia range.

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_2.pdf}
      }
      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
      \label{fig:5}
   \end{figure}

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 1 & OHD & SNe Ia & SNe Ia + QSO 
         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
         \hline
         $\Omega_{2,0}$ & $0.324_{-0.066}^{+0.056}$ & $0.380_{-0.020}^{+0.020}$
          & $0.378_{-0.020}^{+0.020}$ & $0.375_{-0.019}^{+0.019}$
          & $0.298_{-0.007}^{+0.007}$ & $0.308_{-0.007}^{+0.005}$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.08$ & $<-2.73$ & $<-2.75$
         & $<-2.91$ & $<-3.38$  & $<-3.71$ \\
         $\log_{10}(M_x/$GeV) & $>-9.85$ & $>-9.26$ & $>-9.23$
         & $>-9.13$ & $>-8.56$ & $>-8.26$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 1.}
      \label{tab:5}
   \end{table*}

   \begin{figure}[htbp]
      \centering
      \includegraphics[width=0.45\textwidth]{pdf_1.pdf}
      \caption{The probability density of $\Omega_{2,0}$ from different
      datasets.}
      \label{fig:6}
   \end{figure}

@@

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 2 & OHD & SNe Ia & SNe Ia + QSO 
         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
         \hline
         $\Omega_{2,0}$ & $0.299_{-0.074}^{+0.074}$ & $0.216_{-0.078}^{+0.096}$
          & $0.208_{-0.087}^{+0.12}$ & $0.202_{-0.049}^{+0.060}$ 
          & $0.296_{-0.014}^{+0.014}$ & $0.291_{-0.013}^{+0.013}$ \\
         $n$ & $1.5_{-2.9}^{+1.4}$ & $-0.82_{-0.44}^{+0.29}$
          & $-0.85_{-0.49}^{+0.42}$ & $-0.83_{-0.27}^{+0.24}$
          & $-0.40_{-0.29}^{+0.29}$ & $-0.41_{-0.13}^{+0.13}$ \\
         $w_{\text{IDM}}$ & $-1.5_{-0.5}^{+1.0}$ & $-0.73_{-0.10}^{+0.15}$
          & $-0.72_{-0.14}^{+0.16}$ & $-0.72_{-0.08}^{+0.09}$
          & $-0.87_{-0.10}^{+0.10}$ & $-0.86_{-0.04}^{+0.04}$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 2.}
      \label{tab:6}
   \end{table*}
